DNSKEY Management

### 2012-12-05 paper/paper.tex
finshed trust chain descr.

Finally, we will shortly outline the DNSSEC situation in Switzerland
(i.e. the \verb|ch.|  and how its authorities handle DNSKEY management
issues.

@@

DNSSEC trust chains are similar to the ones used in SSL, where an entity marks its trust in another by \emph{signing} its certificate\footnote{Which is nothing more than a public-private key pair with additional metadata.}

Hence, in the real world, the \emph{friend} we trust is the so-called root authority -- the root domain in DNSSEC -- of whom we know the public key in advance.

@@

>>>>

Finally, we will shortly outline the DNSSEC situation in Switzerland
(i.e. the \verb|ch.| zone and how its authorities handle DNSKEY management
issues.

@@

In the DNS world, the \emph{friend} we trust is the so-called root authority -- the root domain in DNSSEC -- of whom we know the public key in advance.

@@

DNSSEC's trust hierarchy is similar to the SSL Certificate infrastructure, where an entity marks its trust in another by \emph{signing} its certificate\footnote{Which is nothing more than a public key with additional metadata.}. However, DNSSEC theoretically only has one single top-authority\footnote{The use of TAR's should remain temporary, as in an ideal setup DNSSEC could work without them.}, while the SSL Certificate hierarchy disposes of many.
